\section{Introduction}

\noindent This document describes how to use and extend the \textbf{F}inite
Element \textbf{F}rame\textbf{W}ork, from here on referred to as
\FFW. The goal of this software package is to provide a tool which presents 
various methods in $2$D in a reference implementation, and to provide a platform for 
future research and development. The target audience consists of students and 
researchers in the field of mathematical finite element research. Therefore, 
the \FFW provides mechanisms for interpreting and visualizing the numerical results, 
and a clean and readable implementation is preferred over performance. Following 
these design goals we have chosen the MATLAB programming language. 

\bigskip

\noindent The \FFW currently features conforming, nonconforming and mixed methods for general 
linear elliptic, and elastic partial differential equations (PDE). The complexity
of the methods ranges from basic linear discretizations for scalar elliptic problems 
to a mixed higher order, locking free discretization for elasticity problems.

\bigskip

\noindent An edge oriented mesh refinement that produces shape regular, nested triangulations with 
no hanging nodes is included in this package. This algorithm is used for local mesh
refinement guided by reliable and efficient residual based error estimators.

\bigskip

\noindent To avoid data redundancy, a global structure containing all computed data, 
including complete mesh information is maintained. Furthermore, this structure 
is used to analyze and to debug methods and to visualize the results. 

\bigskip

\noindent New methods can be verified by analytic model problems which are created automatically using the 
Symbolic Toolbox. Fast and precise numerical Gaussian integration routines of arbitrary order
are included.

