\subsection{Mark}
In order to refine the mesh adaptively we first have to say where.
In difference to other implementations we generally mark only edges 
instead of elements. If we want to refine an element we therefor
have to mark all its edges.
An edge is refined depending on the error estimator.
There are three different contributions to the total estimated error.
There is the error on an edge (etaEd), on an element (etaT) and the 
error on elements that should be refined \emph{bisec5} instead of
\emph{red} (etaOsc). To decide which edges are marked there are four different
strategies.
%
%
\subsubsection{uniform}
\textbf{file:} \path{.\algorithms\mark\uniform.m}\\[1.5ex]
All elements are refined uniformly \emph{red}. Therefore 
all Edges are marked and no elements are marked for \emph{bisec5}.
\begin{pcode}
refineEdges = true(nrEdges,1);
refineElemsBisec5 = false(nrElems,1);
\end{pcode}
%
\subsubsection{maximum}
\textbf{file:} \path{.\algorithms\mark\maximum.m}\\[1.5ex]
The maximum algorithm only mark those edges or elements where
the error is large. In order to decide when the error on an 
edge is to large we use the following rule. The edge or element
$\eta_{i}$ will be marked if 
\begin{equation*}
\eta_{i} >  \theta \cdot \max_{j}\eta_{j}\; .
\end{equation*}
The index $j$ goes over all edges or elements and $\theta$ is 
constant (default: $\theta = 0.5$).
To mark an element means here as above to mark all its edges. 
The matlab code is printed in the next line.
\begin{pcode}
refineEdges = (etaEd > thetaEd * max(etaEd));
\end{pcode}
\code{True} means that the edge is marked and \code{false} it
is not.
The next step in the code realizes that all edges of marked
elements are marked because at the end we only want to have marked edges. 
\begin{pcode}
I = (etaT > thetaT * max(etaT))';
refineElems(I) = true;
refineEdges4e = ed4e(refineElems,:);
refineEdges(refineEdges4e(:)) = true;
\end{pcode}
Elements that should be refined \emph{bisec5}, i.e. have large error
(etaOsc) are treated analogously. The reason why you use \emph{bisec5}
instead of \emph{red} refinement is that with \emph{bisec5} you get
a new node in the interior of the element.\\
The maximum algorithm can be very inefficient. Suppose we have the
same error on each edge except of very few edges and on those edges the error
is very large. Then the maximum algorithm might only refine these few edges 
(cf. figure~\ref{sect:MeshGeneration.Mark.maximum.fig}).

\begin{figure}
\setlength{\unitlength}{6cm}
\begin{picture}(1, 1)
\qbezier(0.1, 0.2)(0.15,0.5)(0.2,0.2)
\qbezier(0.2, 0.2)(0.25,0.25)(0.3,0.2)
\qbezier(0.3, 0.2)(0.35,0.4)(0.4,0.2)
\qbezier(0.4,0.2)(0.45,0.5)(0.5, 0.3)
\qbezier(0.5,0.3)(0.525,0.6)(0.55, 1)
\qbezier(0.55, 1)(0.575,0.6)(0.6, 0.2)
\qbezier(0.6,0.2)(0.65,0.5)(0.7, 0.2)
\qbezier(0.7, 0.2)(0.75,0.4)(0.8,0.2)
\qbezier(0.8, 0.2)(0.85,0.25)(0.9,0.2)
\put(0.05,0.5){\line(1,0){0.9}}
\put(1,0.5){\tiny 0.5 max}
\put(0,0){\vector(0,1){1}}
\put(0,0){\vector(1,0){1}}
\put(1.05,0){\tiny edge or element}
\put(0.05,0.9){\tiny estimated error}
\end{picture}
\caption{The maximum algorithm might mark only a few edges.}
\label{sect:MeshGeneration.Mark.maximum.fig}
\end{figure}


\subsubsection{bulk}
\textbf{file:} \path{.\algorithms\mark\bulk.m}\\[1.5ex]
The bulk algorithm marks edges that satisfy the following condition.
\begin{equation*}
 \sum_{\substack{i\in I\\I\subseteq \{1,\ldots,N\}}}\eta_k^2 \geq  \theta \cdot \sum_{j=1}^{N} \eta_j^2\;.
\end{equation*}
Where $N$ denotes the number of edges or elements.
It is important to see that the set of edges that
are selected by this condition is not unique.
Here we use an greedy approach. We iteratively take
those edges with the largest error. Using this approach 
guarantees that we have the smallest possible set of
marked edges that satisfy the bulk condition.
In the following the corresponding matlab lines are printed.
\begin{pcode}
[sortedEtaEd,I] = sort(etaEd,'descend');
sumEtaEd = cumsum(sortedEtaEd.^2);
k = find(sumEtaEd >= thetaEd * norm(etaEd,2)^2,1,'first');
[sortedEtaT,I] = sort(etaT,'descend');
sumEtaT = cumsum(sortedEtaT.^2);
k = find(sumEtaT >= thetaT * norm(etaT,2)^2,1,'first');
refineElems(I(1:k)) = true;
refineEdges4e = ed4e((refineElems | refineElemsBisec5),:);
refineEdges(refineEdges4e(:)) = true;
\end{pcode}
The problem that only a few edges or element are marked 
like with the maximum algorithm cannot happen here
(cf. Figure~\ref{sect:MeshGeneration.Mark.bulk.fig}).

\begin{figure}
\setlength{\unitlength}{6cm}
\begin{picture}(1, 1)
\qbezier(0.1, 0.2)(0.15,0.5)(0.2,0.2)
\qbezier(0.2, 0.2)(0.25,0.25)(0.3,0.2)
\qbezier(0.3, 0.2)(0.35,0.4)(0.4,0.2)
\qbezier(0.4,0.2)(0.45,0.5)(0.5, 0.3)
\qbezier(0.5,0.3)(0.525,0.6)(0.55, 1)
\qbezier(0.55, 1)(0.575,0.6)(0.6, 0.2)
\qbezier(0.6,0.2)(0.65,0.5)(0.7, 0.2)
\qbezier(0.7, 0.2)(0.75,0.4)(0.8,0.2)
\qbezier(0.8, 0.2)(0.85,0.25)(0.9,0.2)
\put(0.05,0.25){\line(1,0){0.9}}
\put(1,0.25){\tiny bulk}
\put(0,0){\vector(0,1){1}}
\put(0,0){\vector(1,0){1}}
\put(1.05,0){\tiny edge or element}
\put(0.05,0.9){\tiny estimated error}
\end{picture}
\caption{With the bulk algorithm it cannot happen that only
         a few edges are marked.}
\label{sect:MeshGeneration.Mark.bulk.fig}
\end{figure}

\subsubsection{graded}
\textbf{file:} \path{.\algorithms\mark\graded.m}\\[1.5ex]
Refinement with graded grids is a a priori mesh refinement toward singular corner points.
In the past the so called $\beta$-graded grids were very popular. The a priori analysis consists of the following theorem.
%
\begin{theorem}
Let $\mathcal{T}$ be a regular triangulation of $\Omega=T_{ref}$ such that for given $N\in\mathbb{N}$ and $\beta>0$
\begin{enumerate}
\item $\mathcal{T}$ contains the element $T_0=conv\{(0,0),(N^{-\beta},0),(0,N^{-\beta})\}$.
\item For each $T\in \mathcal{T}\backslash\{T_0\}$ and all $x\in T$ one has $diam(T)\leq c\frac{1}{N}|x|^{\beta-1}$
\end{enumerate}
Then, if $\alpha + \beta > 2$, it follows that
\begin{equation*}
|| \nabla(u_{\alpha} - I_{\mathcal{T}}u_{\alpha})||_{L^2(\Omega)}\leq c N^{-min\{1,\alpha\beta\}}\; .
\end{equation*}
where $u_{\alpha}$ is the corner singularity function and $\alpha$ depends on the opening angle in the corner singularity.
\end{theorem}
\noindent
It is known that $\beta$-graded grids satisfy this conditions. But here we follow another approach. We simply refine our mesh with \emph{red}, \emph{green} and \emph{blue} refinement until these conditions are satisfied. This leads to simpler algorithms since $\beta$-graded grids are difficult to implement. Another advantage is that the angles of the triangulation only depend on the initial triangulation.