\section{Mesh Generation}
\label{sect:MeshGeneration}

\noindent The aim of adaptive finite elements is a problem-based generation of a triangulation. This triangulation is then optimal in the sense that it reflects the structure of the problem. Therefore there is the well known AFEM-Loop which consists of the following steps

\begin{align*}
\text{Mark }\Longrightarrow\text{ Refine }\Longrightarrow\text{ Solve }\Longrightarrow\text{Estimate}.
\end{align*}

\noindent In the following we will present a short introduction of the steps \textit{Mark} and \textit{Refine} which are the major steps in construction of triangulations. The \textit{Solve}-step is just solving the linear system of equations. Here we have taken the built-in MATLAB-solver. There is also an iterative solver for the $P_1$-FE, the so-called multigrid solver. This implementation is only a proof of concept and will not be explained further. For readers who are interested in more details we refer to \cite{Bra,HaFaIo}. Here the general concepts of iterative solvers are explained. The \textit{Estimate}-step, which is essential for the \textit{Mark}-step if one has no a~priori knowledge about the problem, consist of the estimation of the error of the discrete solution. A lot of work was done in this field. An exemplary collection of these works is \cite{Brandts,BrCC,CC1,CC2,CC2004,CCFu,CCFu2,CCHo1,CCHo2,Ver}. In the \FFW mostly the residual based error estimator is taken. Since a theoretical treatment of the various estimators is not the aim of this documentation we refer the reader to the literature in bibliography.


\input{sect_MeshGeneration_input}
\input{sect_MeshGeneration_mark}
\input{sect_MeshGeneration_closure}
\input{sect_MeshGeneration_refine}
\input{sect_MeshGeneration_properties}